Assessing the Firing of Ceramic Materials: a Seriation-Based Approach

### 2023-06-09 README.Rmd
Prepare for first release
Add DOI

> Frerebeau, N. (2023). _`r Title`_. _Archéosciences, revue d'Archéométrie_. <https://doi.org/xxx/xxx>

@@

> Frerebeau, N. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

>>>>

> Frerebeau, N. (2023). _`r Title`_. _Archéosciences, revue d'Archéométrie_.

@@

> Frerebeau, N. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.8020137>

@@

### 2023-06-09 analysis/paper/paper.qmd
Add DOI

| **Version** | **Date**   | **Description**            | **DOI** |
|------------:|-----------:|:---------------------------|:--------|
| 0.0.0.9000  |  | Submitted to _Archéosciences_ |  |

>>>>

| **Version** | **Date**   | **Description**            | **DOI** |
|---------:|-----------:|:------------------------------|:---------------------------|
| 1.0.0    | 2023-06-09 | Submitted to _Archéosciences_ | [10.5281/zenodo.8020137](https://doi.org/10.5281/zenodo.8020137) |
